\HeaderA{MIRTG-package}{Two-dimensional compensatory IRT model graphing package}{MIRTG.Rdash.package}
\aliasA{MIRTG}{MIRTG-package}{MIRTG}
\keyword{Package}{MIRTG-package}
\begin{Description}\relax
The package performs to draw the popular graphics of the MIRT in R environment.
\end{Description}
\begin{Details}\relax
\Tabular{ll}{
Package: & MIRT\\
Type: & Package\\
Version: & 1.0\\
Date: & 2009-04-20\\
License: & GPL verson 2 or newer\\
}
Function list of this package:
"MIRT"\\
"vector.plot"\\
"surface.2D"\\
"surface.3D"\\
"contour.plot"\\
"difsurface.2D"\\
"difsurface.3D"\\
"centroid.plot"\\
"clamshell.plot"\\
"direction.plot"\\
"correlation.plot"\\
"inf.2D"\\
"inf.3D"\\
"Angle"\\
The package is built based on package "MASS" and "rgl".\\
Acknowledgement to Dr Matthew Burke and Dr Devdass Sunnassee for the help in the package building process.
\end{Details}
\begin{Author}\relax
Zhan Shu, Terry Ackerman\\
Maintainer: Zhan Shu <z_shu@uncg.edu>
\end{Author}
\begin{References}\relax
Ackerman,T.(1994), Using Multidimensional Item Response Theory to Understand What Items and Tests Are Measuring.Applied Measurement in Education,7(4),255-278.\\
Ackerman,T.(1996),Graphical Representation of Multidimensional Item Response Theory Analyses. Applied Psychological Measurement,20(4),311-329.\\
Ackerman.T, Girel.M,(2003), Using Multidimensional Item Response Theory to Evaluate Educational and Psychological Tests. Educational Measurement: Issues and Practices.\\
Reckase.M, McKinley.R,(1983), The Definition of Difficulty and Discrimination of Multi-dimensional Item Response Theory Model. AERA, Montreal,April.\\
Reckase.M,(1985). The Difficulty of Test Item that Measure more than one Ability. AERR, Chicago, April.\\
Reckase.M, McKinley.R,(1991), The Discriminating Power of Items That Measure More Than One Dimension. Applied Psychological Measurement,15(4),361-373.
\end{References}

